The pollination trade-off

### 2018-12-08 paper/manuscript.Rmd
Paragraph functional originality and #shared pol

Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained. 
Simultaneously, because visitation, pollen production and abundance are correlated, these trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between these factors to increasse conspecific pollen and reduce heterospecific pollen deposition. 
The relative wide range of in our model coefficients might be explained by the wide variation of the extent to which plant species are affected by pollen deposition. 
While some species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985]. 
* We did find a trade-off between the number of partners a species interacts with and the mutualistic service. Interacting with more species alone is often accompanied by a decreases in both the quantity and quality of pollination. 
* However, the effect and importance of this trade-off is comparatively small when considering other factors that describe the species niche and its ecological settings. 
* We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any. This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their own pollen gets deposited on the stigma. Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favours cross-pollination as, evolutionary, it has been shown to be a better strategy than cloning. 
* Overall it seems like density seems to be a dominant force behind pollen transfer. If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is reflected in a smaller amount of deposited pollen. We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen. 
* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentally related to the way we understand and mathematically represent mutualistic systems. 
Some of the most widely used theoretical models of pollination account for the negative effects of mutualism by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree. 
This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
However we show that care must be taken because the negative effects of the mutualistic trade-off in both the quantity and quality of pollination can be offset by density mechanisms. Species with large degrees also tend be abundant and prolific pollen producers.

>>>>

Our results corroborate the importance that previous studies have attributed to the role that visitation and abundance play at determining competition for pollination [@feldman_when_2004; @munoz_presence_2008; @morales_interspecific_2008]. 
The fact that they also involve a trade-off between the quantity and quality of pollination might explain the often contrasting results that these studies, based on two or three species systems obtained. 
Simultaneously, because visitation, pollen production and abundance are correlated, these trade-offs also suggest that to minimise competition for pollination plants must reach a fine balance between these factors to increasse conspecific pollen and reduce heterospecific pollen deposition. 
The relative wide range of in our model coefficients might be explained by the wide variation of the extent to which plant species are affected by pollen deposition. 
While some species experience a large reduction on seed set due to heterospecific pollen deposition, some others are relatively insensitive to heterospecific pollen but are greatly affected by low levels of conspecific pollen deposition [@campbell_mechanism_1985]. 
* We did find a trade-off between the number of partners a species interacts with and the mutualistic service. Interacting with more species alone is often accompanied by a decreases in both the quantity and quality of pollination. 
Two other strategies involved a much smaller trade-off than the abundance or visit efficacy. 
Specifically, having high functional originality relative to other species in the community or sharing few pollinators is benetitial to both the quantity and quality of pollination.
Interestingly, these two strategies also had lower explanatory power in the models of pollen deposition. 
This is not to say that these variables are actually unimportant to pollen deposition, rather it suggest that the processes that underlay them might be more complex than what our metrics are able to capture. 
Especially in what relates to conspecific pollen deposition, which was harder to model than heterospecific pollen. 
On the one hand these two variables are more tighly related to the understanding of competition at the community scale than metrics of dominance. 
On the other, having distinct traits, for example trough phenology differentiation, has a positive impact on the pollination service only to the extent to which previous floral communities have promoted high pollinator densities [@ye_competition_2014]. 
In addition, some plants have been shown possess mechanisms that prevent heterospecific pollen deposition even when shared visitors carry pollen loads from diverse species. 
Similarly, other factors, not meassured in our study, like pollinator behaviour and densities [@ye_competition_2014; ref to Melissa's paper?] or the spatial context [@cariveau_spatially_2009] can also shape the way sharing pollinators affects the pollination service.

* We found that animal pollination only brings a small amount of extra conspecific pollen (compared selfing) if any. This relatively small difference is probably very important because, first, some plants simply aren't self-fertile, even if their own pollen gets deposited on the stigma. Second, in some flowers there is temporary separation in the maturation of the sexes (dichogamy) that favours cross-pollination as, evolutionary, it has been shown to be a better strategy than cloning. 
* Overall it seems like density seems to be a dominant force behind pollen transfer. If you have many individuals of your species, you get fewer visits (dilution of the pollinators flying around), which is reflected in a smaller amount of deposited pollen. We show that abundant plants also tend to comprise a greater component of the pollen source pool and so the end result is that get more conspecific pollen per visit than heterospecific pollen. 
* Our result of the comparatively weak effect of the mutualistic trade-off is important because it is fundamentally related to the way we understand and mathematically represent mutualistic systems. 
Some of the most widely used theoretical models of pollination account for the negative effects of mutualism by adjusting the mutualistic benefit of an interaction so that it can be negatively affected by the number of mutualistic partners---the species degree. 
This approach, considerably simplifies the mathematical treatment of competition for pollinators. 
However we show that care must be taken because the negative effects of the mutualistic trade-off in both the quantity and quality of pollination can be offset by density mechanisms. Species with large degrees also tend be abundant and prolific pollen producers.
